---
title: "Kaggle Survey 2019  - EDA"
author: "Akshaj Verma"
output: html_notebook
---


```{r message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(ggplot2)
library(lubridate)
```


## Read data.
```{r}
mcr_df_2019 <- read_csv("data/kaggle_survey_2019/multiple_choice_responses.csv")
mcr_df_2018 <- read_csv("data/kaggle_survey_2018/multipleChoiceResponses.csv")
# mcr_df_2017 <- read_csv("data/kaggle_survey_2017/multipleChoiceResponses.csv")

questions_df_2019 <- read_csv("data/kaggle_survey_2019/questions_only.csv")
questions_df_2018 <- read_csv("data/kaggle_survey_2018/SurveySchema.csv")
# questions_df_2017 <- read_csv("data/kaggle_survey_2017/schema.csv")

# text_res_df <- read_csv("data/other_text_responses.csv")
# schema_df <- read_csv("data/survey_schema.csv")
```


## Helper Functions


### Create Stats from multi answer choice questions

```{r}
createMultiQuesDF <- function(df, extra_cols, target_col, remove_cols) {
  
  subset_for_target_df <- df %>% select(contains(target_col), -contains(remove_cols))
  
  col_names <- subset_for_target_df %>%
                  map(unique) %>%
                  lapply(function(x) x[!is.na(x)])
  
  names(subset_for_target_df) <- unlist(col_names)
  
  extra_target_binded_df <- cbind(df %>% select(extra_cols), subset_for_target_df)
  
  extra_target_binded_df <- extra_target_binded_df %>%
                              mutate_at((length(extra_cols)+1):ncol(extra_target_binded_df), function(x) if_else(is.na(x), 0, 1)) 

  
  return(extra_target_binded_df)
}
```


## EDA

### 2019 data
```{r}
mcr_df_2019 <- mcr_df_2019 %>% filter(row_number() != 1)
mcr_df_2019 <- mcr_df_2019 %>% rename(
                  time_to_finish = `Time from Start to Finish (seconds)`,
                  age = Q1,
                  gender = Q2,
                  country = Q3,
                  education = Q4,
                  designation = Q5,
                  company_size = Q6,
                  ds_team_size_at_work = Q7,
                  ml_at_company = Q8,
                  yearly_salary = Q10,
                  money_spent_on_ml_last_5_yrs = Q11,
                  data_analysis_tool = Q14,
                  coding_years_to_analyze_data = Q15,
                  recom_prog_lang_to_beginners = Q19,
                  used_tpu = Q22,
                  years_used_ml = Q23
                  )

head(mcr_df_2019)
```

#### Analyse Questions with Multiple Answers
```{r}
createMultiQuesDF(df = mcr_df_2019, extra_cols = c("age", "gender", "country"), target_col = "Q17", remove_cols = "OTHER_TEXT")
```

```{r}
questions_df_2019 %>%
  gather(key = "key", value = "val")
```





#### 2018 data


Q1
Q2
Q3
Q4
Q6
Q9
Q10
Q11
Q12
Q13
Q14
Q15
Q16
Q18
Q19
Q21
Q24
Q25
Q27
Q28
Q29
Q30
Q36
Q38
time_to_finish = `Time from Start to Finish (seconds)`,
                  age = Q1,
                  gender = Q2,
                  country = Q3,
                  education = Q4,
                  designation = Q5,
                  company_size = Q6,
                  ds_team_size_at_work = Q7,
                  ml_at_company = Q8,
                  yearly_salary = Q10,
                  money_spent_on_ml_last_5_yrs = Q11,
                  data_analysis_tool = Q14,
                  coding_years_to_analyze_data = Q15,
                  used_tpu = Q22,
                  years_used_ml = Q23
```{r}
mcr_df_2018 <- mcr_df_2018 %>% filter(row_number() != 1)
mcr_df_2018 <- mcr_df_2018 %>%
                # select(contains(c("Q1","Q2","Q3","Q4","Q6","Q9","Q10","Q11","Q12","Q13","Q14","Q15","Q16","Q18","Q19","Q21","Q24","Q25","Q27","Q28","Q29","Q30","Q36","Q38"))) %>%
                rename(
                  time_to_finish = `Time from Start to Finish (seconds)`,
                  gender = Q1,
                  age = Q2,
                  country = Q3,
                  education = Q4,
                  designation = Q6,
                  yearly_salary = Q9,
                  ml_at_company = Q10,
                  data_analysis_tool = Q12_MULTIPLE_CHOICE,
                  recom_prog_lang_to_beginners = Q18,
                  coding_years_to_analyze_data = Q24, 
                  years_used_ml = Q25
                  )

head(mcr_df_2018)
```

```{r}
mcr_df_2018 %>%
  select(contains(c("gender", "age")))
```

```{r}
createMultiQuesDF(df = mcr_df_2018, extra_cols = c("age", "gender", "country"), target_col = "Q27", remove_cols = "OTHER_TEXT")
```

```{r}
questions_df_2018 %>%
  filter(row_number() == 1) %>%
  select(2:ncol(questions_df_2018)) %>%
  gather(key = "key", value = "val") %>%
  inner_join(questions_df_2019 %>%   gather(key = "key", value = "val"), "val") %>%
  write.csv("combined_ques_1918.csv", row.names = FALSE)
```



